method

### 2021-11-12 06_Paper/ER-ED/method.Rmd
added empty data fames for ER and ED data

datalist_ED = lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"), pattern = '*_ED.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)
```

>>>>

datalist_ED = lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"), pattern = '*_ED.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)

# new empty frame to store files into
data_ER = data.frame(ID = character(), )

data_ED = data.frame(ID = character(), step = double(), choice = character(),
                           LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())
```
